\documentclass[../main.tex]{subfiles}

\begin{document}
	\section{Kinematics}
		\begin{preamb}
			Kinematics is the study of the motion of objects. It can describe the way a thing moves in space over time. We will only cover one-dimensional motion in this chapter.
		\end{preamb}
	
		\subsection{Distance and Displacement}
		\pdef{Distance}{The distance traversed by an object in some time is the entire distance regardless of the direction of motion. The SI unit of distance is the metre [\si{\meter}].}
		Distances are a \textit{scalar} quantity.
		
		\pdef{Displacement}{The displacement of an object is the \textbf{net change in position} of an object. The SI unit of displacement is the meter [\si{\meter}].}
		Displacements are a \textit{vector} quantity. When reporting the displacement of an object, it is important to also state the \textbf{direction} from the origin point.
		
		\subsection{Average Speed, Average Velocity, and Instantaneous Velocity}
		\peqn{Average Speed}{The average speed of an object is given as}{\text{average speed} = \frac{\text{total distance}}{\text{total time}}}
		Speed is a \textit{scalar} quantity.
		
		\pdef{Average Velocity}{The average velocity of an object is the change in displacement of the object from the origin point. The SI unit of velocity is metre per second [\si{\meter\per\second}].}
		
		\peqn{Average Velocity}{The average velocity of an object can be computed as}{\langle v \rangle = \frac{\Sigma s}{\Sigma t}}
		
		\pdef{Instantaneous Velocity}{The instantaneous velocity of an object is the rate of change of displacement of the object at \textbf{some specific time}. Mathematically, it is the derivative of the displacement function.}
		
		\peqn{Instantaneous Velocity}{The instantaneous velocity at a time \(t\) is computed as}{v(t) = \lim_{\Delta t \to 0} \frac{\Delta s}{\Delta t}}
		Velocity is a \textit{vector} quantity. When reporting the velocity of an object, it is important to also state the \textbf{direction} from the origin point.
		\subsection{Acceleration}
		\pdef{Acceleration}{Acceleration is the rate of change of velocity.}
		\peqn{Acceleration}{The acceleration of an object is computed as}{a = \frac{\Delta v}{\Delta t}}
		Acceleration is a \textit{vector} quantity. When reporting the acceleration of an object, the direction from the origin point must be stated.
		
		\subsection{Kinematic Graphs}
		A kinematic graph is a visual representation of the state of motion of the object over a period of time. A kinematic graph is useful in many situations, and should be drawn when you are stuck in a kinematics problem.
		
		\subsubsection{Displacement-time Graph}
		The displacement-time graph records the displacement of an object over a time period. The displacement is recorded on the vertical axis, the time is recorded on the horizontal axis.
		
		\begin{center}
			\begin{tikzpicture}
			\pgfplotsset{ticks=none}
			\begin{axis}[
				axis lines = middle,
				xlabel = \(t\),
				ylabel = \(s\),
				ymin = 0
			]
				\addplot [domain=0:10] {x^3};
				\addplot [gray, domain=0:10] {168.75*x - 843.75};
				\filldraw (axis cs:7.5, 421.875) circle (0.25mm);
				\draw [dashed, gray] (axis cs: 7, 337.5) -- (axis cs: 8,337.5) -- (axis cs: 8,506.25);
			\end{axis}
		\end{tikzpicture}
		\begin{framed}
			The gradient of the tangent to the displacement-time graph is the velocity at that time only.
		\end{framed}
		\end{center}
		
		The gradient of a displacement-time graph tells us its \textbf{velocity}.
		
		\subsubsection{Velocity-time Graph}	
		The velocity-time graph records the velocity of an object over a time period. The velocity is recorded on the vertical axis, the time is recorded on the horizontal axis.
		
		\begin{center}
			\begin{tikzpicture}
			\pgfplotsset{ticks=none}
			\begin{axis}[
				axis lines = middle,
				xlabel = \(t\),
				ylabel = \(v\)
			]
				\addplot [name path=x, domain=0:10] {0};
				\addplot [domain=0:10] {3*x^2};
				\addplot [name path=v, domain=0:5] {3*x^2} \closedcycle;
				\addplot [
        			fill = gray,
        			fill opacity = 0.5,
    			] fill between[
        			of=x and v,
    			];
			\end{axis}
			\end{tikzpicture}
			\begin{framed}
				Usually the graph would be made out of straight lines and calculating area shouldn't be a problem. If the graph is curved, count squares.
			\end{framed}
		\end{center}
		
		The gradient of a velocity-time graph tells us its \textbf{acceleration}; the area under a velocity-time graph tells us the \textbf{displacement}.
		
		\subsection{Freefall}
		\pdef{Freefall}{An object is in freefall when the only force acting on it is due to gravity.}
		This means that the acceleration due to freefall is always equal to the local acceleration \(g\), and all other forces like air drag do not exist.
		\begin{center}
			\begin{tikzpicture}
				\filldraw (0,0) circle (0.75mm);
				\draw [line width=0.5mm, -stealth] (0,0) -- (0,-2) node[pos=0.5, anchor=west] {\(mg\)};
				\draw [->>] (2,-0.5) -- (2,-1) node[anchor=west] {\(g\)};
				\draw (2,-1) -- (2,-1.5);
			\end{tikzpicture}
		\end{center}
		
		\begin{center}
			\begin{tikzpicture}
			\pgfplotsset{ticks=none}
			\begin{axis}[
			axis lines = middle,
			xlabel = \(t\),
			ylabel = \(v\),
			ymax=100
			]
			\addplot [domain=0:10] {10*x};
			\draw [gray, dashed] (axis cs: 1,10) -- (axis cs: 9,10) -- (axis cs: 9,90);
			\node at (axis cs: 5,15) {gradient = \SI{10}{\meter \second^{-2}}};
			\end{axis}
			\end{tikzpicture}
		\end{center}
	
		\subsection{Air drag}
		In real situations, air drag, or air resistance, is a resistive force that works against the weight of an object when falling. Air drag is \textbf{proportional to the square of the velocity} of an object.
		
		As an object falls, its velocity increases. Air drag then also increases. The acceleration of the object slowly decreases as the net force acting on the object is decreasing. 
		
		This continues until a point where the air drag is equal and opposite to the weight of the object. The object then experiences zero net force, and has zero acceleration, maintaining a constant velocity. 
		
		This constant velocity is \textbf{terminal velocity}.
		\begin{center}
			\begin{tikzpicture}
			\filldraw (0,0) circle (0.75mm);
			\draw [line width=0.5mm, -stealth] (0,0) -- (0,-2) node[pos=0.5, anchor=west] {\(mg\)};
			\draw [line width=0.5mm, -stealth] (0,0) -- (0,0.5) node[pos=0.5, anchor=west] {\(F_\mathrm{drag}\)};
			\draw [->>] (2,-0.5) -- (2,-1) node[anchor=west] {\(g\)};
			\draw (2,-1) -- (2,-1.5);
			\end{tikzpicture}
		\end{center}
		\begin{center}
			\begin{tikzpicture}
				\pgfplotsset{ticks=none}
				\begin{axis}[
					axis lines = middle,
					ymax = 20,
					xlabel = \(t\),
					ylabel = \(v\)
					]
					\addplot [domain=0:4] {-x*(x-8)};
					\addplot [domain=4:8] {16};
					\draw [gray, dashed] (axis cs: 0,16) -- (axis cs: 4,16) node[pos=0.5, anchor=south, black] {\(v_\mathrm{terminal}\)};
				\end{axis}
			\end{tikzpicture}
		\end{center}
		
\end{document}